Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-14 paper/paper.tex
minor change in IV.A (prioritization)

Considering prioritization, we classified warnings in two kinds,
reflecting their likelihood of manifesting a real bug. Warnings of the
kind ``\hi{}'' are associated with the cases where the test code
executed to completion without violating any internal checks, but it
violated assertions declared in the test itself or its harness. The
rationale is that the input is more likely to be valid as it it did
not raise exceptions during the execution of the application code,
but, it manifests discrepancy through violation of an assertion
declared in the test. In contrast, warnings in the ``\lo{}'' group are
more likely to be asssociated with invalid inputs. They reflect the
cases where the anomaly is observed during the execution of functions,
which are part of the application. We found that different engines
often check pre-conditions of those functions differently. It can
happen, for example, that one engine enforces a weaker pre-condition
on a function input compared to another engine and that is
acceptable. For instance, it is acceptable to pass values greater than
\Fix{x} to function \CodeIn{\Fix{WWW}} in \Fix{y} but not in
\Fix{z}. In those cases, the infrastructure would observe a
discrepancy that is more likely to be associated with an invalid input
produced by the fuzzer, \ie{}, it is likely to be a bug in the test
code not the engine (library or runtime) code. It is worth noting that
``\lo'' warnings can be bug
revealing. Figure~\ref{fig:lo-truepositive} shows one of these
cases. In this example, the test instantiates an \CodeIn{ArrayBuffer}
object and stores an 8-bit integer at the 0 position. According to the
specification~\cite{ecmas262-getviewvalue}, a \CodeIn{RangeError}
exception should be thrown if a negative value is passed to the
function \CodeIn{ToIndex}, indirectly called by the test case. In this
case, however, the \chakra{} engine did not throw any exception, which
violates the spec. This bug was fixed by developers after our bug
report and is no longer present in the most recent release of
\chakra. Despite that counter-example, most bugs we found emerged from
``\hi{}'' warnings.

>>>>

We classified warnings in two types,
reflecting their likelihood of manifesting a real bug. Warnings of the
kind ``\hi{}'' are associated with the cases where the test code
executed to completion without violating any internal checks, but it
violated assertions declared in the test itself or its harness. The
rationale is that the input is more likely to be valid as it it did
not raise exceptions during the execution of the application code,
but, it manifested discrepancy through the violation of an assertion
declared in the test. In contrast, warnings of type ``\lo{}'' are
more likely to be asssociated with invalid inputs. They reflect the
cases where the anomaly is observed during the execution of functions,
which are part of the application. We found that different engines
often check pre-conditions of those functions differently. It can
happen, for example, that one engine enforces a weaker pre-condition
on a function input compared to another engine and that is
acceptable.\Comment{ For instance, it is acceptable to pass values greater than
\Fix{x} to function \CodeIn{\Fix{WWW}} in \Fix{y} but not in
\Fix{z}.} In those cases, the infrastructure would observe a
discrepancy that is more likely to be associated with an invalid input
produced by the fuzzer, \ie{}, it is likely to be a bug in the test
code not the engine (library or runtime) code. However, as expected, our heuristic
is not precise---``\lo'' warnings can 
reveal bugs. Figure~\ref{fig:lo-truepositive} shows one of these
cases. In this example, the test instantiates an \CodeIn{ArrayBuffer}
object and stores an 8-bit integer at the 0 position. According to the
specification~\cite{ecmas262-getviewvalue}, a \CodeIn{RangeError}
exception should be thrown if a negative value is passed to the
function \CodeIn{ToIndex}, indirectly called by the test case. In this
case, however, the \chakra{} engine did not throw any exception, which
violates the spec. This case of undocumented precondition, reported
and handled by developers as a bug, was fixed by developers after our bug
report and is no longer present in the most recent release of
\chakra. Despite that case, most bugs we found emerged from
``\hi{}'' warnings.
